Shift-sensitive Power Transformations for Transforming Data to Normality

### 2023-02-23 manuscript/manuscript.Rmd
Update manuscript.Rmd

@@

  parallel::clusterExport(
    cl=cl,
    varlist = c(".compute_robust_lambda", ".optimisation_inner")
  )

  parallel::parLapplyLB(
    cl = cl,
    X = experiments,
    fun = .optimisation_outer,
    data = x,
    chunk.size = 1L)

  # Stop cluster.
  parallel::stopCluster(cl)
}

>>>>

        for(transformation_method in transformation_methods){
          for(robustness_weighting_function in c("step", "triangle", "cosine")){

@@

  # 
  # 
  # # Start cluster
  # cl <- parallel::makeCluster(18L)
  # 
  # parallel::clusterExport(
  #   cl=cl,
  #   varlist = c(".compute_robust_lambda", ".optimisation_inner")
  # )
  # 
  # parallel::parLapplyLB(
  #   cl = cl,
  #   X = experiments,
  #   fun = .optimisation_outer,
  #   data = x,
  #   chunk.size = 1L)
  # 
  # # Stop cluster.
  # parallel::stopCluster(cl)
}
